Governing through patronage: the bargain for education in decentralized Brazil

### 2020-11-16 paper/paper.tex
fixed descriptive for school principals

Table \ref{tbl:descriptive_teacher} provides some additional descriptive statistics regarding teachers. The teacher labor force is highly educated and primarily composed of women, and schools in Brazil are relatively small, with an average of 4 teachers per school. As for school principals, while

>>>>

Table \ref{tbl:descriptive_teacher} provides some additional descriptive statistics regarding teachers. The teacher labor force is highly educated and primarily composed of women, and schools in Brazil are relatively small, withttps://askubuntu.com/questions/487527/give-specific-user-permission-to-write-to-a-folder-using-w-notationh an average of 4 teachers per school. As for school principals, while
